---
title: "Application to 2016 Election Data"
output: 
  pdf_document:
    keep_tex: true
header-includes:
  - \usepackage{stackengine}
  - \usepackage{rotating}
---

```{r setup, include=FALSE}
rm(list = ls())
## WEIGHTING A 2016 PRE-ELECTION SURVEY

### Packages
library(tidyverse)
library(survey)
library(knitr)
library(kableExtra)

#devtools::install_github("chadhazlett/KBAL", ref = "master") 
library(kbal)
```


```{r setup_params}
## Erin's path
path_data = "~/Dropbox/Documents/2019__2020/work/kpop/2016_reweighting_example/data/"
path_data = "../data/"
```

```{r useful_functions}
vote_contrast <- quote((recode_vote_2016Democrat - recode_vote_2016Republican) /
                           (recode_vote_2016Democrat + recode_vote_2016Republican))

### Function for creating targets from auxiliary information and formula
create_targets <- function (target_design, target_formula) {
    target_mf <- model.frame(target_formula, model.frame(target_design))
    target_mm <- model.matrix(target_formula, target_mf)
    wts <- weights(target_design)
    colSums(target_mm * wts) / sum(wts)
}

```

## Load Data

```{r}
## SURVEY DATA (PEW)
### Load
###This needs to be loaded from dropbox/local not github bc it's too big
pew <- readRDS(paste0(path_data, "pew.rds"))

## AUXILIARY INFORMATION (CCES)
### Load
#This needs to be loaded from dropbox/local not github bc it's too big
cces <- readRDS(paste0(path_data, "cces.rds"))
### Drop invalid cases
cces <- cces %>%
    filter((CC16_401 == "I definitely voted in the General Election.") &
               !is.na(commonweight_vv_post))

## make recode_educ_white column
cces <- cces %>%
  mutate(recode_educ_white = 
           factor(case_when(recode_race == "White" ~ as.character(recode_educ),
                            TRUE ~ "No Split"), 
                  levels = c(levels(cces$recode_educ), "No Split")),
         commonweight_vv_post = commonweight_vv_post / mean(commonweight_vv_post))



pew <- pew %>%
  mutate(recode_educ_white = 
           factor(case_when(recode_race == "White" ~ as.character(recode_educ),
                            TRUE ~ "No Split"), 
                  levels = c(levels(pew$recode_educ), "No Split")))

### Actual results
pres <- readRDS(paste0(path_data, "election.rds"))

natl_margin <- pres %>%
    summarise(margin = (sum(demtotal) - sum(reptotal)) /
                  (sum(demtotal) + sum(reptotal))) %>%
    as.numeric()
natl_margin
```

```{r define_models}
formula_rake_demos_noeduc <- ~recode_age_bucket + recode_female + 
    recode_race + recode_region + recode_pid_3way
formula_rake_demos_weduc <- ~recode_age_bucket + recode_female + 
  recode_race + recode_region + recode_educ + recode_pid_3way
formula_ps <- ~recode_age_3way + recode_female + recode_race +
    recode_region + recode_educ_3way + recode_pid_3way
formula_retrospective <- ~recode_age_bucket:recode_pid_3way + 
  recode_female:recode_pid_3way+
    recode_race_educ_reg:recode_pid_3way
```

```{r make_svydesign, warning = FALSE}
## Find Missing Strata
## Make "strata" variable in CCES and Pew
cces <- bind_cols(cces, cces %>% 
                    unite("strata", all.vars(formula_ps), remove = FALSE) %>%
                    unite("strata_wage", c(all.vars(formula_ps), "recode_age"), 
                          remove = FALSE) %>%
                    select(strata, strata_wage))

pew <- bind_cols(pew, pew %>% 
                   unite("strata", all.vars(formula_ps), remove = FALSE) %>%
                   unite("strata_wage", c(all.vars(formula_ps), "recode_age"), 
                         remove = FALSE) %>%
                   select(strata, strata_wage))


missing_strata <- unique(cces$strata)[!(unique(cces$strata) %in% unique(pew$strata))]

## recode missing age
pew$recode_age[is.na(pew$recode_age)] <- mean(cces$recode_age, na.rm = TRUE)
cces$recode_age[is.na(cces$recode_age)] <- mean(cces$recode_age, na.rm = TRUE)

### Make survey designs

## For Pew, since there are no design weights, assume SRS
pew_srs <- svydesign(ids = ~1, data = pew)
cces_awt <- svydesign(ids = ~1, weights = ~commonweight_vv_post, data = cces)
```

```{r population_targets}
### Population targets
targets_rake_demos_noeduc <- create_targets(cces_awt, formula_rake_demos_noeduc)
targets_rake_demos_weduc <- create_targets(cces_awt, formula_rake_demos_weduc)
targets_retrospective <- create_targets(cces_awt, formula_retrospective)
```

```{r do_calibration}

## Raking on demographics, excluding education
rake_demos_noeduc <- calibrate(design = pew_srs,
                       formula = formula_rake_demos_noeduc,
                       population = targets_rake_demos_noeduc,
                       calfun = "raking")

rake_demos_noeduc <- svydesign(~1, data = pew, weights = weights(rake_demos_noeduc))

## Raking on demographics, including education
rake_demos_weduc <- calibrate(design = pew_srs,
                              formula = formula_rake_demos_weduc,
                              population = targets_rake_demos_weduc,
                              calfun = "raking")

rake_demos_weduc <- svydesign(~1, data = pew, weights = weights(rake_demos_weduc))

## Post-stratification
targets_ps <- svytable(formula = ~strata, 
                       design = subset(cces_awt, !(strata %in% missing_strata)))

post_stratification <- postStratify(design = pew_srs,
                         strata = ~strata,
                         population = targets_ps)

post_stratification <- svydesign(~1, data = pew, 
                                 weights = weights(post_stratification))

## Retrospective weighting scheme
rake_retrospective <- calibrate(design = pew_srs,
                              formula = formula_retrospective,
                              population = targets_retrospective,
                              calfun = "raking",
                              force = TRUE)

rake_retrospective <- svydesign(~1, data = pew, weights = weights(rake_retrospective))
```

```{r kpop}
#############################################
##### PUT FINAL KPOP CODE HERE
#############################################

load("./cleaned data/Full SVD/weights_wPid_full.Rdata")

kpop <- svydesign(~1, data = pew, weights = wts_wPid[, "wtkbal_b.5x"])
kpop_mf <- svydesign(~1, data = pew, weights = wts_wPid[, "wtkbal_mf_b2x"])
```

```{r check_margins}
margin_summary <- round(cbind(cces = svymean(formula_rake_demos_weduc, cces_awt),
                              unweighted = svymean(formula_rake_demos_weduc, pew_srs),
            rake_demos_noeduc = svymean(formula_rake_demos_weduc, rake_demos_noeduc),
            rake_demos_weduc = svymean(formula_rake_demos_weduc, rake_demos_weduc),
            post_stratification = svymean(formula_rake_demos_weduc, post_stratification),
            rake_retrospective = svymean(formula_rake_demos_weduc, rake_retrospective),
            kpop = svymean(formula_rake_demos_weduc, kpop),
            kpop_mf = svymean(formula_rake_demos_weduc, kpop_mf)) * 100, 1) %>%
  data.frame() %>%
  rownames_to_column() %>%
  mutate(variable = case_when(str_detect(rowname, "age") ~ "4-way Age Bucket",
                             str_detect(rowname, "female") ~ "Gender",
                             str_detect(rowname, "race") ~ "Race/Ethnicity",
                             str_detect(rowname, "region") ~ "Region",
                             str_detect(rowname, "educ") ~ "Education Level",
                             str_detect(rowname, "pid") ~ "Party Identification",
                             TRUE ~ "Empty"),
         level = 
           gsub("recode_|age_bucket|female|race|region|educ|pid_3way", "", rowname)) %>%
  select(level, everything(), -rowname, -variable)
```

```{r margins_table, echo = FALSE, results = 'asis'}
margin_summary %>%
  mutate(level = str_replace(level, "graduate", "")) %>%
  kable(format = "latex", booktabs = T,
        col.names = linebreak(
          c("", "\\belowbaseline[0ex]{\\rotatebox{90}{\\parbox{1.1in}{\\raggedright{Target (CCES)}}}}", 
          "\\belowbaseline[0ex]{\\rotatebox{90}{\\parbox{1.1in}{\\raggedright{Unweighted Pew}}}}",
          "\\belowbaseline[0ex]{\\rotatebox{90}{\\parbox{1.1in}{\\raggedright{Raking:\\\\Demographics}}}}",
          "\\belowbaseline[0ex]{\\rotatebox{90}{\\parbox{1.1in}{\\raggedright{Raking:\\\\Demographics + Education}}}}",
          "\\belowbaseline[0ex]{\\rotatebox{90}{\\parbox{1.1in}{\\raggedright{Post-Stratification}}}}", 
          "\\belowbaseline[0ex]{\\rotatebox{90}{\\parbox{1.1in}{\\raggedright{Raking:\\\\Retrospective}}}}", 
          "\\belowbaseline[0ex]{\\rotatebox{90}{\\parbox{1.1in}{\\raggedright{KPop}}}}", 
          "\\belowbaseline[0ex]{\\rotatebox{90}{\\parbox{1.1in}{\\raggedright{KPop Mean First}}}}")), 
        escape = FALSE,
<<<<<<< HEAD
        caption = "Marginal distribution of important demographics under different weighting models.") %>%
=======
        caption = "Marginal distribution, in precentage points, of important demographics under different weighting models.") %>%
>>>>>>> d3d385ec5ff13d4996e94ae3eeeec6e9e736dd90
  column_spec(2:ncol(margin_summary), width = "0.45in") %>%
  column_spec(1, width = "1.45in") %>%
  kable_styling() %>%
  pack_rows("4-way Age Bucket", 1, 4, latex_gap_space = "0.5em") %>%
  pack_rows("Gender", 5, 6, latex_gap_space = "0.5em") %>%
  pack_rows("Race/Ethnicity", 7, 10, latex_gap_space = "0.5em") %>%
  pack_rows("Region", 11, 14, latex_gap_space = "0.5em") %>%
  pack_rows("Education Level", 15, 20, latex_gap_space = "0.5em") %>%
  pack_rows("Party Identification", 21, 23, latex_gap_space = "0.5em")%>%
  footnote(general = "Cells present the percentage of the population represented by each variable level.",
           threeparttable = T)
```

```{r summarize_missing}
## Total missing strata
sum(cces$commonweight_vv_post[cces$strata %in% missing_strata])/sum(cces$commonweight_vv_post)


round(cbind(cces = svymean(formula_rake_demos_weduc, cces_awt),
            not_missing = svymean(formula_rake_demos_weduc, 
                                  subset(cces_awt, !(strata %in% missing_strata))),
            missing = svymean(formula_rake_demos_weduc, 
                              subset(cces_awt, (strata %in% missing_strata)))) * 100, 1) %>%
  data.frame() %>%
  rownames_to_column() %>%
  mutate(variable = case_when(str_detect(rowname, "age") ~ "4-way Age Bucket",
                             str_detect(rowname, "female") ~ "Gender",
                             str_detect(rowname, "race") ~ "Race/Ethnicity",
                             str_detect(rowname, "region") ~ "Region",
                             str_detect(rowname, "educ") ~ "Education Level",
                             str_detect(rowname, "pid") ~ "Party Identification",
                             TRUE ~ "Empty"),
         level = 
           gsub("recode_|age_bucket|female|race|region|educ|pid_3way", "", rowname)) %>%
  select(level, everything(), -rowname, -variable)
```

```{r check_margins_white_educ}
margin_summary_educ <- round(cbind(cces = svymean(~recode_educ_white, cces_awt),
                              unweighted = svymean(~recode_educ_white, pew_srs),
            rake_demos_noeduc = svymean(~recode_educ_white, rake_demos_noeduc),
            rake_demos_weduc = svymean(~recode_educ_white, rake_demos_weduc),
            post_stratification = svymean(~recode_educ_white, post_stratification),
            rake_retrospective = svymean(~recode_educ_white, rake_retrospective),
            kpop = svymean(~recode_educ_white, kpop),
            kpop_mf = svymean(~recode_educ_white, kpop_mf)) * 100, 1) %>%
  data.frame() %>%
  rownames_to_column() %>%
  mutate(variable = case_when(str_detect(rowname, "age") ~ "4-way Age Bucket",
                             str_detect(rowname, "female") ~ "Gender",
                             str_detect(rowname, "race") ~ "Race/Ethnicity",
                             str_detect(rowname, "region") ~ "Region",
                             str_detect(rowname, "educ") ~ "Education Level",
                             str_detect(rowname, "pid") ~ "Party Identification",
                             TRUE ~ "Empty"),
         level = 
           gsub("recode_|age_bucket|female|race|region|educ|pid_3way|educ_3way|_white", 
                "", rowname)) %>%
  select(level, everything(), -rowname, -variable)
```

```{r margins_table_educ, echo = FALSE, results = 'asis', warnings = FALSE}
options(knitr.kable.NA = '--')
margin_summary_educ <- margin_summary_educ %>%
  mutate(level = str_replace(level, "graduate", "")) %>%
  filter(level != "No Split") %>%
  mutate(p_strata = cces / sum(cces))


educ_mae_w <- margin_summary_educ %>% select(-level) %>%
              summarize_all(funs(mae_w = sum(abs(. - cces)  * p_strata))) %>%
  rename_all(funs(gsub("_mae_w", "", .))) %>%
  mutate(level = "Mean Absolute Error",
         cces = NA)

margin_summary_educ <- bind_rows(margin_summary_educ,
                                 educ_mae_w) %>%
  select(-p_strata)
  
margin_summary_educ %>%
  kable(format = "latex", booktabs = T, digits = 1,
        col.names = linebreak(
          c("", "\\belowbaseline[0ex]{\\rotatebox{90}{\\parbox{1.1in}{\\raggedright{Target (CCES)}}}}", 
          "\\belowbaseline[0ex]{\\rotatebox{90}{\\parbox{1.1in}{\\raggedright{Unweighted Pew}}}}",
          "\\belowbaseline[0ex]{\\rotatebox{90}{\\parbox{1.1in}{\\raggedright{Raking:\\\\Demographics}}}}",
          "\\belowbaseline[0ex]{\\rotatebox{90}{\\parbox{1.1in}{\\raggedright{Raking:\\\\Demographics + Education}}}}",
          "\\belowbaseline[0ex]{\\rotatebox{90}{\\parbox{1.1in}{\\raggedright{Post-Stratification}}}}", 
          "\\belowbaseline[0ex]{\\rotatebox{90}{\\parbox{1.1in}{\\raggedright{Raking:\\\\Retrospective}}}}", 
          "\\belowbaseline[0ex]{\\rotatebox{90}{\\parbox{1.1in}{\\raggedright{KPop}}}}", 
          "\\belowbaseline[0ex]{\\rotatebox{90}{\\parbox{1.1in}{\\raggedright{KPop Mean First}}}}")), 
        escape = FALSE,
        caption = "Marginal distribution of education level for white voters under different weighting models.") %>%
  column_spec(2:ncol(margin_summary), width = "0.45in") %>%
  column_spec(1, width = "1.68in") %>%
  kable_styling() %>%
  pack_rows("Education Level for White Voters", 1, 6, latex_gap_space = "0.5em") %>%
  pack_rows("Error", 7, 7, latex_gap_space = "0.5em") %>%
  footnote(general = "Cells present the percentage of the population represented by each variable level.  Mean absolute error is the absoluate error in each cell, relative to the target (CCES), weighted by the edcuation level's proportion among white voters in the target population.",
           threeparttable = T)
```

```{r make_results}
target_margin <- svycontrast(svymean(~recode_vote_2016, cces_awt, na.rm = TRUE),
                       vote_contrast)[1]

svymean(~recode_vote_2016, rake_demos_noeduc, deff = TRUE)

comp_df <- data.frame(
    cces = svycontrast(svymean(~recode_vote_2016, 
                               cces_awt, na.rm = TRUE),
                       vote_contrast),
    unweighted = svycontrast(svymean(~recode_vote_2016, 
                                     pew_srs, na.rm = TRUE),
                        vote_contrast),
    rake_demos_noeduc = svycontrast(svymean(~recode_vote_2016, 
                                            rake_demos_noeduc, na.rm = TRUE),
                        vote_contrast),
    rake_demos_weduc = svycontrast(svymean(~recode_vote_2016, 
                                           rake_demos_weduc, na.rm = TRUE),
                        vote_contrast),
    post_stratification = svycontrast(svymean(~recode_vote_2016, 
                                              post_stratification, na.rm = TRUE),
                        vote_contrast),
    rake_retrospective = svycontrast(svymean(~recode_vote_2016, 
                                             rake_retrospective, na.rm = TRUE),
                        vote_contrast),
    kpop = svycontrast(svymean(~recode_vote_2016, 
                               kpop, na.rm = TRUE),
                        vote_contrast),
    kpop_mf = svycontrast(svymean(~recode_vote_2016, 
                                  kpop_mf, na.rm = TRUE),
                        vote_contrast)) %>%
    pivot_longer(cols = everything(),
                 names_to = c("source", ".value"), 
                 names_pattern = "(.*)\\.(.*)") %>%
    rename(est = nlcon) %>%
    mutate(est = est * 100,
           SE = SE * 100,
           err_target = est - target_margin * 100,
           source = str_replace(source, "_", " "),
           source_name = factor(source, labels = c("Target (CCES)", 
                                              "KPop", 
                                              "KPop + Mean First",
                                              "Post-Stratification", 
                                              "Raking\nDemographics\nwithout Education", 
                                              "Raking\nDemographics\nwith Education", 
                                              "Raking\nRetrospective", 
                                              "Pew\nUnweighted"),
                           ordered = TRUE))

comp_df
```

```{r plot_results, echo = FALSE}
comp_df %>%
    ggplot() +
    aes(x = source_name, y = est, ymin = est - 1.96*SE, ymax = est + 1.96*SE) +

    geom_hline(yintercept = c(0, natl_margin * 100, comp_df$est[comp_df$source == "cces"]),
               linetype = c("solid", "dashed", "longdash"),
               color = c("black", "gray60", "black")) +
    geom_pointrange() +
    scale_y_continuous(breaks = round(c(natl_margin * 100, seq(-5, 10, 5)), 1),
                       minor_breaks = NULL,
                       labels = scales::percent_format(scale = 1, accuracy = 0.1)) +
    theme_bw() +
    theme(plot.title = element_text(hjust = 0.5)) +

    labs(x = NULL, y = "Estimated Margin (95% CI)") +
    ggtitle("Estimates of Clinton National Popular Vote Margin") +
    theme(axis.text.x = element_text(angle = 55, hjust = 1)) +
    annotate(geom = "text", x = 8.65, y = natl_margin * 100, label = " True\n National\n Margin", hjust = 0, angle = -90, color = "gray60", size = 3.5) +
    annotate(geom = "text", x = 8.55, y = comp_df$est[comp_df$source == "cces"], label = " CCES Estimated\n Margin", hjust = 0, angle = 90, size = 3.5) +
    theme(legend.title = element_blank()) +
  scale_x_discrete(limits=comp_df$source_name, expand = expansion(0, 1.2))
```

```{r save_plot}
ggsave("./plots/weighted_pew_results.pdf", width = 6, height = 4)
```

Note from `survey` package:

The design effect compares the variance of a mean or total to the variance from a study of the same size using simple random sampling without replacement. Note that the design effect will be incorrect if the weights have been rescaled so that they are not reciprocals of sampling probabilities. To obtain an estimate of the design effect comparing to simple random sampling with replacement, which does not have this requirement, use `deff="replace"`. This with-replacement design effect is the square of Kish's "deft".

```{r design_effect}
lapply(list(rake_demos_noeduc, rake_demos_weduc, post_stratification, rake_retrospective, kpop, kpop_mf), 
       function(x) {
         svymean(~recode_vote_2016, x, deff = "replace")
       })
```




## Weights

Looking at the average weight in margins.


```{r check_weights}

load("cleaned data/Full SVD/weights_wPid_full.Rdata")
#optimal choice w pid: no mf = 0.5, mf = 2
weights <- pew %>% select(recode_age_bucket,
                          recode_age_3way,
                          recode_female,
                          recode_race,
                          recode_region,
                          recode_educ,
                          recode_educ_3way,
                          recode_pid_3way,
                          recode_race_educ_reg)  %>%
    mutate(rake_demos_noeduc_wt = weights(rake_demos_noeduc)/
                                 mean(weights(rake_demos_noeduc)),
           rake_demos_weduc_wt = weights(rake_demos_weduc)/
                                 mean(weights(rake_demos_weduc)),
           post_stratification_wt = weights(post_stratification)/
                                 mean(weights(post_stratification)),
           rake_retrospective_wt = weights(rake_retrospective)/
                                 mean(weights(rake_retrospective)),
           k_wt = wts_wPid$wtkbal_b.5x,
           k_mf_wt = wts_wPid$wtkbal_mf_b2x)

#just checking everything is internally consistent
#sum(weights$rake_demos_noeduc_wt != wts_wPid$wt1_pid)

age <- weights %>% 
    group_by(recode_age_bucket) %>% 
    summarise(mu_1 = mean(rake_demos_noeduc_wt),
              mu_2 = mean(rake_demos_weduc_wt),
              mu_3 = mean(post_stratification_wt),
              mu_4 = mean(rake_retrospective_wt),
              mu_kpop = mean(k_wt),
              mu_kpop_mf = mean(k_mf_wt)) %>% ungroup()

female <- weights %>% 
    group_by(recode_female) %>% 
    summarise(mu_1 = mean(rake_demos_noeduc_wt),
              mu_2 = mean(rake_demos_weduc_wt),
              mu_3 = mean(post_stratification_wt),
              mu_4 = mean(rake_retrospective_wt),
              mu_kpop = mean(k_wt),
              mu_kpop_mf = mean(k_mf_wt)) %>% ungroup()

race <- weights %>% 
    group_by(recode_race) %>% 
    summarise(mu_1 = mean(rake_demos_noeduc_wt),
              mu_2 = mean(rake_demos_weduc_wt),
              mu_3 = mean(post_stratification_wt),
              mu_4 = mean(rake_retrospective_wt),
              mu_kpop = mean(k_wt),
              mu_kpop_mf = mean(k_mf_wt)) %>% ungroup()

region <- weights %>% 
    group_by(recode_region) %>%
    summarise(mu_1 = mean(rake_demos_noeduc_wt),
              mu_2 = mean(rake_demos_weduc_wt),
              mu_3 = mean(post_stratification_wt),
              mu_4 = mean(rake_retrospective_wt),
              mu_kpop = mean(k_wt),
              mu_kpop_mf = mean(k_mf_wt)) %>% ungroup()

education <- weights %>% 
    group_by(recode_educ) %>% 
    summarise(mu_1 = mean(rake_demos_noeduc_wt),
              mu_2 = mean(rake_demos_weduc_wt),
              mu_3 = mean(post_stratification_wt),
              mu_4 = mean(rake_retrospective_wt),
              mu_kpop = mean(k_wt),
              mu_kpop_mf = mean(k_mf_wt)) %>% ungroup()

pid <- weights %>% 
    group_by(recode_pid_3way) %>% 
    summarise(mu_1 = mean(rake_demos_noeduc_wt),
              mu_2 = mean(rake_demos_weduc_wt),
              mu_3 = mean(post_stratification_wt),
              mu_4 = mean(rake_retrospective_wt),
              mu_kpop = mean(k_wt),
              mu_kpop_mf = mean(k_mf_wt)) %>% ungroup()


colnames(age) <- c("Variable", colnames(age)[-1])
colnames(female)<- c("Variable", colnames(female)[-1])
colnames(race)<- c("Variable", colnames(race)[-1])
colnames(region) <- c("Variable", colnames(region)[-1])
colnames(education) <- c("Variable", colnames(education)[-1])
colnames(pid) <- c("Variable", colnames(pid)[-1])

weights_summary <- rbind(age, female, race, region, education, pid) 

```



```{r weights_print, echo = F, results = "asis"}

weights_summary %>% 
  mutate(Variable = str_replace(Variable, "graduate", "")) %>%
  kable(format = "latex", booktabs = T,
        col.names = linebreak(
          c("", 
            "\\belowbaseline[0ex]{\\rotatebox{90}{\\parbox{1.1in}{\\raggedright{Raking \\\\Demographics without Education }}}}",
          "\\belowbaseline[0ex]{\\rotatebox{90}{\\parbox{1.1in}{\\raggedright{Raking \\\\Demographics with Education }}}}",
          "\\belowbaseline[0ex]{\\rotatebox{90}{\\parbox{1.1in}{\\raggedright{Post-Stratification}}}}", 
          "\\belowbaseline[0ex]{\\rotatebox{90}{\\parbox{1.1in}{\\raggedright{Raking Retrospective}}}}", 
          "\\belowbaseline[0ex]{\\rotatebox{90}{\\parbox{1.1in}{\\raggedright{KPop}}}}", 
          "\\belowbaseline[0ex]{\\rotatebox{90}{\\parbox{1.1in}{\\raggedright{KPop Mean First}}}}")), 
        escape = FALSE,  digits= 3,
        caption = "Mean weights of important demographics under different weighting models .") %>%
  column_spec(2:ncol(weights_summary), width = "0.45in") %>%
  column_spec(1, width = "1.45in") %>%
  kable_styling() %>%
  pack_rows("4-way Age Bucket", 1, 4, latex_gap_space = "0.5em") %>%
  pack_rows("Gender", 5, 6, latex_gap_space = "0.5em") %>%
  pack_rows("Race/Ethnicity", 7, 10, latex_gap_space = "0.5em") %>%
  pack_rows("Region", 11, 14, latex_gap_space = "0.5em") %>%
  pack_rows("Education Level", 15, 20, latex_gap_space = "0.5em") %>%
  pack_rows("Party Identification", 21, 23, latex_gap_space = "0.5em")%>%
  footnote(general = "Cells present the average weight used to reweight the Pew sample to the CCES target population in each variable level.",
           threeparttable = T)


```



