---
title: "Application to 2016 Election Data"
output: 
  pdf_document:
    keep_tex: true
header-includes:
  - \usepackage{stackengine}
  - \usepackage{rotating}
---

```{r setup, include=FALSE}
rm(list = ls())
## WEIGHTING A 2016 PRE-ELECTION SURVEY

### Packages
library(tidyverse)
library(survey)
library(knitr)
library(kableExtra)

#devtools::install_github("chadhazlett/KBAL", ref = "master") 
library(kbal)
```


```{r setup_params}
## Erin's path
#path_data = "~/Dropbox/Documents/2019__2020/work/kpop/2016_reweighting_example/data/"
#Ciara's 
#path_data = "../data/"
path_data = "/Users/Ciara/Dropbox/kpop/2016_reweighting_example/data/"
```

```{r useful_functions}
vote_contrast <- quote((recode_vote_2016Democrat - recode_vote_2016Republican) /
                           (recode_vote_2016Democrat + recode_vote_2016Republican))

### Function for creating targets from auxiliary information and formula
create_targets <- function (target_design, target_formula) {
    target_mf <- model.frame(target_formula, model.frame(target_design))
    target_mm <- model.matrix(target_formula, target_mf)
    wts <- weights(target_design)
    colSums(target_mm * wts) / sum(wts)
}

```

## Load Data

```{r}
## SURVEY DATA (PEW)
### Load
pew <- readRDS(paste0(path_data, "pew.rds"))

## AUXILIARY INFORMATION (CCES)
### Load
cces <- readRDS(paste0(path_data, "cces.rds"))
### Drop invalid cases
cces <- cces %>%
    filter((CC16_401 == "I definitely voted in the General Election.") &
               !is.na(commonweight_vv_post))

## make recode_educ_white column
cces <- cces %>%
  mutate(recode_educ_white = 
           factor(case_when(recode_race == "White" ~ as.character(recode_educ),
                            TRUE ~ "No Split"), 
                  levels = c(levels(cces$recode_educ), "No Split")))

pew <- pew %>%
  mutate(recode_educ_white = 
           factor(case_when(recode_race == "White" ~ as.character(recode_educ),
                            TRUE ~ "No Split"), 
                  levels = c(levels(pew$recode_educ), "No Split")))

### Actual results
pres <- readRDS(paste0(path_data, "election.rds"))

natl_margin <- pres %>%
    summarise(margin = (sum(demtotal) - sum(reptotal)) /
                  (sum(demtotal) + sum(reptotal))) %>%
    as.numeric()
natl_margin
```

```{r age_NA}
## recode missing age
#mean(cces$recode_age, na.rm = TRUE)
#mean(pew$recode_age, na.rm = TRUE)
#sum(is.na(pew$recode_age))
#sum(is.na(cces$recode_age))
#####XXXXXX issue here
#pew$recode_age_bucket[is.na(pew$recode_age)]
pew$recode_age_3way[is.na(pew$recode_age)] <- "a_18to50"
pew$recode_age_bucket[is.na(pew$recode_age)] <- "18 to 35"
pew$recode_age[is.na(pew$recode_age)] <- mean(pew$recode_age, na.rm = TRUE)
cces$recode_age[is.na(cces$recode_age)] <- mean(cces$recode_age, na.rm = TRUE)


```


```{r define_models}
formula_rake_demos_noeduc <- ~recode_age_bucket + recode_female + 
    recode_race + recode_region + recode_pid_3way
formula_rake_demos_weduc <- ~recode_age_bucket + recode_female + 
  recode_race + recode_region + recode_educ + recode_pid_3way
formula_ps <- ~recode_age_3way + recode_female + recode_race +
    recode_region + recode_educ_3way + recode_pid_3way
formula_retrospective <- ~recode_age_bucket:recode_pid_3way + 
  recode_female:recode_pid_3way+
    recode_race_educ_reg:recode_pid_3way
```

```{r make_svydesign, warning = FALSE}
## Find Missing Strata
## Make "strata" variable in CCES and Pew
cces <- bind_cols(cces, cces %>% 
                    unite("strata", all.vars(formula_ps), remove = FALSE) %>%
                    unite("strata_wage", c(all.vars(formula_ps), "recode_age"), 
                          remove = FALSE) %>%
                    select(strata, strata_wage))

pew <- bind_cols(pew, pew %>% 
                   unite("strata", all.vars(formula_ps), remove = FALSE) %>%
                   unite("strata_wage", c(all.vars(formula_ps), "recode_age"), 
                         remove = FALSE) %>%
                   select(strata, strata_wage))


missing_strata <- unique(cces$strata)[!(unique(cces$strata) %in% unique(pew$strata))]


### Make survey designs

## For Pew, since there are no design weights, assume SRS
pew_srs <- svydesign(ids = ~1, data = pew)
cces_awt <- svydesign(ids = ~1, weights = ~commonweight_vv_post, data = cces)
```

```{r population_targets}
### Population targets
targets_rake_demos_noeduc <- create_targets(cces_awt, formula_rake_demos_noeduc)
targets_rake_demos_weduc <- create_targets(cces_awt, formula_rake_demos_weduc)
targets_retrospective <- create_targets(cces_awt, formula_retrospective)
```

```{r do_calibration}

## Raking on demographics, excluding education
rake_demos_noeduc <- calibrate(design = pew_srs,
                       formula = formula_rake_demos_noeduc,
                       population = targets_rake_demos_noeduc,
                       calfun = "raking")

rake_demos_noeduc <- svydesign(~1, data = pew, weights = weights(rake_demos_noeduc))

## Raking on demographics, including education
rake_demos_weduc <- calibrate(design = pew_srs,
                              formula = formula_rake_demos_weduc,
                              population = targets_rake_demos_weduc,
                              calfun = "raking")

rake_demos_weduc <- svydesign(~1, data = pew, weights = weights(rake_demos_weduc))

## Post-stratification
targets_ps <- svytable(formula = ~strata, 
                       design = subset(cces_awt, !(strata %in% missing_strata)))

post_stratification <- postStratify(design = pew_srs,
                         strata = ~strata,
                         population = targets_ps)

post_stratification <- svydesign(~1, data = pew, 
                                 weights = weights(post_stratification))

## Retrospective weighting scheme
#failed to converge? XX
rake_retrospective <- calibrate(design = pew_srs,
                              formula = formula_retrospective,
                              population = targets_retrospective,
                              calfun = "raking",
                              force = TRUE)

rake_retrospective <- svydesign(~1, data = pew, weights = weights(rake_retrospective))
```

```{r kpop, cache = T, warning= F }

kpop_data <- rbind(pew %>% select(recode_age,
                                  recode_female,
                                  recode_race, 
                                  recode_region, 
                                  recode_pid_3way,
                                  recode_educ, 
                                  recode_age_bucket),
                   cces %>% select(recode_age, 
                                   recode_female, 
                                   recode_race, 
                                   recode_region,
                                   recode_pid_3way, 
                                   recode_educ,
                                   recode_age_bucket)) %>%
   model.matrix(as.formula("~. - 1"), .)


kpop_sampled <- c(rep(1, nrow(pew)), rep(0, nrow(cces)))


kpop_mf_b2x <- kbal(allx=kpop_data,
                      sampled = kpop_sampled,
                      b = 2 * ncol(kpop_data),
                      incrementby = 1,
                      fullSVD = TRUE,
                      meanfirst = TRUE,
        population.w = cces$commonweight_vv_post/mean(cces$commonweight_vv_post),
                      sampledinpop = FALSE,
                      ebal.convergence = TRUE, 
                      printprogress = FALSE)

kpop_b.5x <- kbal(allx=kpop_data,
                    sampled = kpop_sampled,
                    b = 0.5 * ncol(kpop_data),
                    fullSVD = TRUE,
                    meanfirst = FALSE,
                    incrementby = 1,
    population.w = cces$commonweight_vv_post /mean(cces$commonweight_vv_post),
                    sampledinpop = FALSE,
                    printprogress = TRUE)

```
 
```{r kpop_load, echo = F}
#kpop <- svydesign(~1, data = pew, weights = kpop_b.5x$w[kpop_sampled] )
#kpop_mf <- svydesign(~1, data = pew, weights = kpop_mf_b2x$w[kpop_sampled])

load("./cleaned data/Full SVD/weights_wPid_full.Rdata")
kpop <- svydesign(~1, data = pew, weights = wts_wPid[, "wtkbal_b.5x"])
kpop_mf <- svydesign(~1, data = pew, weights = wts_wPid[, "wtkbal_mf_b2x"])
#load("./cleaned data/Full SVD/fullruns_noKsvd.Rdata")
```



```{r make_results}
target_margin <- svycontrast(svymean(~recode_vote_2016, cces_awt, na.rm = TRUE),
                       vote_contrast)[1]

svymean(~recode_vote_2016, rake_demos_noeduc, deff = TRUE)

comp_df <- data.frame(
    cces = svycontrast(svymean(~recode_vote_2016, 
                               cces_awt, na.rm = TRUE),
                       vote_contrast),
    unweighted = svycontrast(svymean(~recode_vote_2016, 
                                     pew_srs, na.rm = TRUE),
                        vote_contrast),
    rake_demos_noeduc = svycontrast(svymean(~recode_vote_2016, 
                                            rake_demos_noeduc, na.rm = TRUE),
                        vote_contrast),
    rake_demos_weduc = svycontrast(svymean(~recode_vote_2016, 
                                           rake_demos_weduc, na.rm = TRUE),
                        vote_contrast),
    post_stratification = svycontrast(svymean(~recode_vote_2016, 
                                              post_stratification, na.rm = TRUE),
                        vote_contrast),
    rake_retrospective = svycontrast(svymean(~recode_vote_2016, 
                                             rake_retrospective, na.rm = TRUE),
                        vote_contrast),
    kpop = svycontrast(svymean(~recode_vote_2016, 
                               kpop, na.rm = TRUE),
                        vote_contrast),
    kpop_mf = svycontrast(svymean(~recode_vote_2016, 
                                  kpop_mf, na.rm = TRUE),
                        vote_contrast)) %>%
    pivot_longer(cols = everything(),
                 names_to = c("source", ".value"), 
                 names_pattern = "(.*)\\.(.*)") %>%
    rename(est = nlcon) %>%
    mutate(est = est * 100,
           SE = SE * 100,
           err_target = est - target_margin * 100,
           source = str_replace(source, "_", " "),
           source_name = factor(source, labels = c("Target (CCES)", 
                                              "KPop", 
                                              "KPop + Mean First",
                                              "Post-Stratification", 
                                              "Raking\nDemographics\nwithout Education", 
                                              "Raking\nDemographics\nwith Education", 
                                              "Raking\nRetrospective", 
                                              "Pew\nUnweighted"),
                           ordered = TRUE))

comp_df
comp_df_rebucket$est -comp_df$est
comp_df_rebucket <- comp_df
```

```{r plot_results, echo = FALSE}
comp_df %>%
    ggplot() +
    aes(x = source_name, y = est, ymin = est - 1.96*SE, ymax = est + 1.96*SE) +

    geom_hline(yintercept = c(0, natl_margin * 100, comp_df$est[comp_df$source == "cces"]),
               linetype = c("solid", "dashed", "longdash"),
               color = c("black", "gray60", "black")) +
    geom_pointrange() +
    scale_y_continuous(breaks = round(c(natl_margin * 100, seq(-5, 10, 5)), 1),
                       minor_breaks = NULL,
                       labels = scales::percent_format(scale = 1, accuracy = 0.1)) +
    theme_bw() +
    theme(plot.title = element_text(hjust = 0.5)) +

    labs(x = NULL, y = "Estimated Margin (95% CI)") +
    ggtitle("Estimates of Clinton National Popular Vote Margin") +
    theme(axis.text.x = element_text(angle = 55, hjust = 1)) +
    annotate(geom = "text", x = 8.65, y = natl_margin * 100, label = " True\n National\n Margin", hjust = 0, angle = -90, color = "gray60", size = 3.5) +
    annotate(geom = "text", x = 8.55, y = comp_df$est[comp_df$source == "cces"], label = " CCES Estimated\n Margin", hjust = 0, angle = 90, size = 3.5) +
    theme(legend.title = element_blank()) +
  scale_x_discrete(limits=comp_df$source_name, expand = expansion(0, 1.2))
```

```{r save_plot}
ggsave("./plots/weighted_pew_results.pdf", width = 6, height = 4)
```

Note from `survey` package:

The design effect compares the variance of a mean or total to the variance from a study of the same size using simple random sampling without replacement. Note that the design effect will be incorrect if the weights have been rescaled so that they are not reciprocals of sampling probabilities. To obtain an estimate of the design effect comparing to simple random sampling with replacement, which does not have this requirement, use `deff="replace"`. This with-replacement design effect is the square of Kish's "deft".

```{r design_effect}
lapply(list(rake_demos_noeduc, rake_demos_weduc, post_stratification, rake_retrospective, kpop, kpop_mf), 
       function(x) {
         svymean(~recode_vote_2016, x, deff = "replace")
       })
```




## Weights

Looking at the average weight in margins.


```{r check_weights}

load("cleaned data/Full SVD/weights_wPid_full.Rdata")
#optimal choice w pid: no mf = 0.5, mf = 2
weights <- pew %>% select(recode_age_bucket,
                          recode_age_3way,
                          recode_female,
                          recode_race,
                          recode_region,
                          recode_educ,
                          recode_educ_3way,
                          recode_pid_3way,
                          recode_race_educ_reg)  %>%
    mutate(rake_demos_noeduc_wt = weights(rake_demos_noeduc)/
                                 mean(weights(rake_demos_noeduc)),
           rake_demos_weduc_wt = weights(rake_demos_weduc)/
                                 mean(weights(rake_demos_weduc)),
           post_stratification_wt = weights(post_stratification)/
                                 mean(weights(post_stratification)),
           rake_retrospective_wt = weights(rake_retrospective)/
                                 mean(weights(rake_retrospective)),
           k_wt = wts_wPid$wtkbal_b.5x,
           k_mf_wt = wts_wPid$wtkbal_mf_b2x)

#just checking everything is internally consistent
#sum(weights$rake_demos_noeduc_wt != wts_wPid$wt1_pid)

age <- weights %>% 
    group_by(recode_age_bucket) %>% 
    summarise(mu_1 = mean(rake_demos_noeduc_wt),
              mu_2 = mean(rake_demos_weduc_wt),
              mu_3 = mean(post_stratification_wt),
              mu_4 = mean(rake_retrospective_wt),
              mu_kpop = mean(k_wt),
              mu_kpop_mf = mean(k_mf_wt)) %>% ungroup()

female <- weights %>% 
    group_by(recode_female) %>% 
    summarise(mu_1 = mean(rake_demos_noeduc_wt),
              mu_2 = mean(rake_demos_weduc_wt),
              mu_3 = mean(post_stratification_wt),
              mu_4 = mean(rake_retrospective_wt),
              mu_kpop = mean(k_wt),
              mu_kpop_mf = mean(k_mf_wt)) %>% ungroup()

race <- weights %>% 
    group_by(recode_race) %>% 
    summarise(mu_1 = mean(rake_demos_noeduc_wt),
              mu_2 = mean(rake_demos_weduc_wt),
              mu_3 = mean(post_stratification_wt),
              mu_4 = mean(rake_retrospective_wt),
              mu_kpop = mean(k_wt),
              mu_kpop_mf = mean(k_mf_wt)) %>% ungroup()

region <- weights %>% 
    group_by(recode_region) %>%
    summarise(mu_1 = mean(rake_demos_noeduc_wt),
              mu_2 = mean(rake_demos_weduc_wt),
              mu_3 = mean(post_stratification_wt),
              mu_4 = mean(rake_retrospective_wt),
              mu_kpop = mean(k_wt),
              mu_kpop_mf = mean(k_mf_wt)) %>% ungroup()

education <- weights %>% 
    group_by(recode_educ) %>% 
    summarise(mu_1 = mean(rake_demos_noeduc_wt),
              mu_2 = mean(rake_demos_weduc_wt),
              mu_3 = mean(post_stratification_wt),
              mu_4 = mean(rake_retrospective_wt),
              mu_kpop = mean(k_wt),
              mu_kpop_mf = mean(k_mf_wt)) %>% ungroup()

pid <- weights %>% 
    group_by(recode_pid_3way) %>% 
    summarise(mu_1 = mean(rake_demos_noeduc_wt),
              mu_2 = mean(rake_demos_weduc_wt),
              mu_3 = mean(post_stratification_wt),
              mu_4 = mean(rake_retrospective_wt),
              mu_kpop = mean(k_wt),
              mu_kpop_mf = mean(k_mf_wt)) %>% ungroup()


colnames(age) <- c("Variable", colnames(age)[-1])
colnames(female)<- c("Variable", colnames(female)[-1])
colnames(race)<- c("Variable", colnames(race)[-1])
colnames(region) <- c("Variable", colnames(region)[-1])
colnames(education) <- c("Variable", colnames(education)[-1])
colnames(pid) <- c("Variable", colnames(pid)[-1])

weights_summary <- rbind(age, female, race, region, education, pid) 

```



```{r weights_print, echo = F, results = "asis"}

weights_summary %>% 
  mutate(Variable = str_replace(Variable, "graduate", "")) %>%
  kable(format = "latex", booktabs = T,
        col.names = linebreak(
          c("", 
            "\\belowbaseline[0ex]{\\rotatebox{90}{\\parbox{1.1in}{\\raggedright{Raking \\\\Demographics without Education }}}}",
          "\\belowbaseline[0ex]{\\rotatebox{90}{\\parbox{1.1in}{\\raggedright{Raking \\\\Demographics with Education }}}}",
          "\\belowbaseline[0ex]{\\rotatebox{90}{\\parbox{1.1in}{\\raggedright{Post-Stratification}}}}", 
          "\\belowbaseline[0ex]{\\rotatebox{90}{\\parbox{1.1in}{\\raggedright{Raking Retrospective}}}}", 
          "\\belowbaseline[0ex]{\\rotatebox{90}{\\parbox{1.1in}{\\raggedright{KPop}}}}", 
          "\\belowbaseline[0ex]{\\rotatebox{90}{\\parbox{1.1in}{\\raggedright{KPop Mean First}}}}")), 
        escape = FALSE,  digits= 3,
        caption = "Mean weights of important demographics under different weighting models .") %>%
  column_spec(2:ncol(weights_summary), width = "0.45in") %>%
  column_spec(1, width = "1.45in") %>%
  kable_styling() %>%
  pack_rows("4-way Age Bucket", 1, 4, latex_gap_space = "0.5em") %>%
  pack_rows("Gender", 5, 6, latex_gap_space = "0.5em") %>%
  pack_rows("Race/Ethnicity", 7, 10, latex_gap_space = "0.5em") %>%
  pack_rows("Region", 11, 14, latex_gap_space = "0.5em") %>%
  pack_rows("Education Level", 15, 20, latex_gap_space = "0.5em") %>%
  pack_rows("Party Identification", 21, 23, latex_gap_space = "0.5em")%>%
  footnote(general = "Cells present the average weight used to reweight the Pew sample to the CCES target population in each variable level.",
           threeparttable = T)


```



